Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Fig 2 set.

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL -> logfit_plot

@@

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL-> movrates_used

@@

ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "np")) %>% 
  # bind_rows(., ppi.summ.df %>% 
  #             dplyr::select(av.disp, dsprsn, model) %>% 
  #             mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          #"ppi",
                                          #"np_1", "np_2", "np_3",
                                          "np"))) -> disp_df

cpr.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., ppr.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., npr.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "npr")) %>% 
  mutate(model = factor(model, levels = c("cpr", "ppr",
                                          "npr"))) -> disp_r_df
```

>>>>

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  NULL -> logfit_plot

@@

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  NULL-> movrates_used

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model)) %>% 
  mutate(model = factor(model, levels = c("cp", "pp","np"))) -> disp_df
```
